Methods for Large Scale Learning to Rank

### 2014-02-27 report/RelatedWork.tex
BoostingTree

>>>>

\section{BoostingTree}
Kocsis et al\cite{Kocsis2013} propose way to train multiple weak learners in parallel and extend those models that are likely to yield a good model when combined through boosting. Authors showed through theoretical analysis that the proposed algorithm asymptotically achieve equal performance to regular boosting. Using this parallel BoostingTree algorithm \ac{GBDT} models could be trained in parallel.
